Data Splitting And Its Applications

### 2019-11-13 summaryThesis.tex
PL is done + part of KM

In this thesis, we propose methodologies to deal with such problems using the so-called data splitting. In a nutshell, data splitting means to split the difficult (sometimes infeasible) job of modelling the big dataset by splitting it into smaller chunks of manageable sub-data, analyze each of them separately, and then combine the results of these analyses using appropriate combinations rules. This would break a difficult task into several, often so-called embarrassingly parallel by computer scientists, simpler tasks. The data splitting approach consists of 3 steps:
\begin{enumerate}
\item Splitting the data.
\item Performing the analysis on each sub-dataset.
\item Efficiently combine the results from each sub-dataset to form an overall estimate with its precision.
\end{enumerate}

@@

For each of these splitting strategies appropriate and efficient combination rules are developed. We also have considered exceptional cases where the general mythologies would fail. Our findings are motivated and supported by various datasets. Furthermore, the methodologies we have developed are implemented in statistical computing language R.
\vspace{1cm}
\begin{center}
{\large{Professional Background}}
\end{center}
\vspace{0.5cm}
Vahid Nassiri  has obtained a Bachelor in Statistics (2002) from the Shahid Beheshti Univerity in Tehran, Iran, and a master in Mathematical Statistics (2008) from the Amirkabir University of Technology in Tehran, Iran. Afterwards, he has obtained a PhD in Applied Mathematics (2013) from Vrije Universiteit Brussel (VUB), Brussels, Belgium. His main research interests are in the field of Big Data and High-dimensional problems. While working on the sparse estimation of high-dimensional linear models in sense of least squares and quantile regression in his former PhD, his current work is concerned on the fast computation of models for correlated data with possible missing values. His research expertise is mainly concerned with analyzing incomplete big correlated data using mixed models, multiple imputation, penalized likelihood and related topics. He also has experiences in consultation involving projects from pharmacology, biology, medicine, engineering, psychology, sociology, linguistics, and market research. He is now working as a statistical consultant in Open Analytics NV, Antwerp, Belgium.

>>>>

In this thesis, we propose methodologies to deal with such problems using the so-called data splitting. In a nutshell, data splitting means to split the difficult (sometimes infeasible) job of modelling the big dataset by splitting it into smaller chunks of manageable sub-data, analyze each of them separately, and then combine the results of these analyses using appropriate combinations rules. This would break a difficult task into several, often so-called embarrassingly parallel, simpler tasks. The data splitting approach consists of 3 steps:
\begin{enumerate}
\item Splitting the data.
\item Performing the analysis on each sub-dataset.
\item Efficiently combine the results from each sub-dataset to form an overall estimate with its precision.
\end{enumerate}

@@

For each of these splitting strategies appropriate and efficient combination rules are developed. We also have considered exceptional cases where the general methodologies would fail. Our findings are motivated and supported by various datasets. Furthermore, the methodologies we have developed are implemented in statistical computing language R.
\vspace{1cm}
\begin{center}
{\large{\textbf{Professional Background}}}
\end{center}
\vspace{0.5cm}
Vahid Nassiri  has obtained a Bachelor in Statistics (2002) from the Shahid Beheshti Univerity in Tehran, Iran, and a master in Mathematical Statistics (2008) from the Amirkabir University of Technology in Tehran, Iran. Afterwards, he has obtained a PhD in Applied Mathematics (2013) from Vrije Universiteit Brussel (VUB), Brussels, Belgium. His main research interests are in the field of Big Data and High-dimensional problems. While working on the sparse estimation of high-dimensional linear models in sense of least squares and quantile regression in his former PhD, his current work is concerned on the fast computation of models for correlated data with possible missing values. His research expertise is mainly concerned with analyzing incomplete big correlated data using mixed models, multiple imputation, penalized likelihood and related topics. He also has experiences in consultation involving projects from pharmacology, biology, medicine, engineering, psychology, sociology, linguistics, and market research. He is now working as a statistical consultant in Open Analytics NV, Antwerp, Belgium.
